---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# prelude

<!-- badges: start -->
<!-- badges: end -->

The goal of `prelude` is to help setup the development environment for users and provide helpers
for connections, authentication and other common objects needed in their analytic workflow.

## Installation

You can install the development version of prelude like so:

``` {r install}
# install.packages("pak")
# pak::pkg_install("asenetcky/prelude")
```

## Authentication

Users in their production environment with their keyring already setup will have easy access
to the authentication related credentials.

```{r example}
library(prelude)

auth <- prelude::grab_prelude_auth()

auth
```


## Connections

Users who already have their dsns setup with generic names like prod, stg, and dev
will have easy access to them.  `prelude` provides easy access to the different connections.

```{r}
prod <- prelude::grab_prod_conn()
stg <- prelude::grab_stg_conn()
dev <- prelude::grab_dev_conn()

prod
stg
dev
```

## Errors and Placeholders

If users are not in the expected production environment `prelude` will use
fake placeholders instead, and `purrr::safely` capture any errors for
users to handle as they see fit.

```{r}
errors <- grab_prelude_errors()

errors$auth$message
errors$conn$message
```

## Environment

`prelude` loads the prelude object into the empty environment, named
`the` on package attachment. The `the` environment is built at compile
time and is not directly available to developers during run time. 
However, they will be able to access the contents of prelude through 
the exported `grab` family of functions.
